---
title: "Probability Theory"
author: "Ananya Saha"
---

# Probability

## Assignment I
Probabilities in terms of the likelihood of events occurring:

- P(T): Probability of being on time.
- P(T'): Probability of not being on time.
- P(S): Probability of a change in scope.
- P(S'): Probability of no change in scope.

Probability tree for the events "Being on time (T)" and "Change in scope (S)" along with conditional probabilities:
```{css}
           P(S)                                P(S') 
             |                                   |
      ______________                      ______________
     |              |                    |              |
  P(T|S)        P(T'|S)               P(T|S')       P(T'|S') 
     |              |                    |              |
   T ∩ S          T' ∩ S              T ∩ S'         T' ∩ S'

```

- P(T ∩ S) = P(S) × P(T ∣ S)
- P(T ∩ S') = P(S') × P(T ∣ S')
- P(T' ∩ S) = P(S) × P(T' ∣ S)
- P(T' ∩ S') = P(S') × P(T' ∣ S')

The probabilities and the sum:

```{r}
# Assigning given values
T_S <- 0.2
T0_S <- 0.8
T_S0 <- 0.6
T0_S0 <- 0.4
S <- 0.3
S0 <- 0.7

# Computing required probabilities
P_T_S <- T_S * S
P_T_S0 <- T_S0 * S0
P_T0_S <- T0_S * S
P_T0_S0 <- T0_S0 * S0
P_SUM <- P_T_S + P_T_S0 + P_T0_S + P_T0_S0

print(P_T_S)
print(P_T_S0)
print(P_T0_S)
print(P_T0_S0)
print(P_SUM)
```

# Set Theory

## Assignment II
With reference to the given Venn Diagram:
* What is the percentage of customers using all three devices?
    + 0,5%
* What is the percentage of customers using at least two devices?
    + (0,5 + 3,3 + 7,3 + 8,8)% = 19,9%
* What is the percentage of customers using only one device?
    + (100 - 19,9)% = 80,1%
    
## Assignment III
To assess the usefulness of the tool in practice we want to know the following probabilities:

1. What is the probability that when the alarm is triggered the product is found to be flawless?
2. What is the probability that when the alarm is triggered the product is found to have flaws?

```{r}
# Assigning given values
P_BA <- 0.97
P_BA0 <- 0.01
P_A <- 0.04
P_A0 <- 1 - P_A

# Following Bayes Theorem,
P_B <- P_BA * P_A + P_BA0 * P_A0
P_AB <- (P_BA * P_A) / P_B
P_A0B <- (P_BA0 * P_A0) / P_B

# Required answer (1)
print(P_A0B)
# Required answer (2)
print(P_AB)

```
These results show that in case the alarm is triggered, there is a possibility of about **19,83%** that the product is flawless and a probability of **80,17%** that the product is faulty.    
