---
title: "Statistical Concepts"
author: "Ananya Saha"
---

## Assignment
1. For each variable, the following values are:
- Expected value
- Variance
- Standard deviation
```{r}

random_vars <- readRDS("data/random_vars.rds")

x1_mean <- mean(random_vars$age)
x1_var <- var(random_vars$age)
x1_sd <- sd(random_vars$age)
x2_mean <- mean(random_vars$income)
x2_var <- var(random_vars$income)
x2_sd <- sd(random_vars$income)

# Expected value x1
print(x1_mean)

# Variance x2
print(x1_var)

# Standard deviation x1
print(x1_sd)

# Expected value x2
print(x2_mean)

# Variance x2
print(x2_var)

# Standard deviation x2
print(x2_sd)

```
2. It makes sense to compare the standard deviations because it measures the dispersion of a random variable, as we see here that the dispersion of the income is larger than that of age.

3. Examining the relationship between both variables and computing
- Covariance
- Correlation

```{r}
covariance <- cov(random_vars$age, random_vars$income)
correlation <- cor(random_vars$age, random_vars$income)
cat("Covariance: ", covariance, "\n")
cat("Correlation: ", correlation, "\n")
```
4. Measure that is easier to interpret: Correlation, having values between -1 and +1, is easier. 

5. Computing the conditional expected values: 
```{r}
subset_minors <- subset(random_vars, age <= 18)
subset_adults <- subset(random_vars, age >= 18 & age <= 65)
subset_seniors <- subset(random_vars, age >= 65)
mean_minors <- mean(subset_minors$income)
mean_adults <- mean(subset_adults$income)
mean_seniors <- mean(subset_seniors$income)

# E[income | age <= 18]
print(mean_minors)

# E[income | age ∈ [18, 65)]
print(mean_adults)

# E[income | age >= 65]
print(mean_seniors)
```