---
title: "Regression and Statistical Inference"
author: "Ananya Saha"
---

## Assignment
1. Checking the Dimensions:
```{r}
df <- readRDS("data/car_prices.rds")
cat("The dimensions are ", dim(df), "\n")
```

2. Detailed look at the Data types:
```{r}
str(df)
```
Data types: Numbers and Strings

Numbers have decimal or float numbers and are different from Strings which can contain alphabets alone, or alphanumeric or special characters and must be within quotes.

3. Linear regression to determine factors relevant for the pricing of a car:
```{r}

model <- lm(price ~., data = df)
summary(model)

min_rpm <- min(df$peakrpm)
max_rpm <- max(df$peakrpm)
```

4. Regressor chosen - peakrpm:
- The attribute "peakrpm" is numeric and takes values between 4200 and 6600.
- Peak RPM means the maximum revolutions the car's engine will be able to perform per minute.
The coefficient estimate is positive and the effect on its price increases when peakrpm increases.
- Yes, its effect is statistically significant and is indicated by the p-value. Since the p-value is small, that implies a high statistical significance.

5. Regression after adding a new variable:
```{r}
library(tidyverse)
df <- df %>%
  mutate(seat_heating = TRUE)

summary(df)

model <- lm(price ~., data = df)
summary(model)
```
Coefficient for the new variable seat_heating: the model matrix will become singular as all values are TRUE and constant, thus resulting in an error.
