---
title: "Directed Acyclic Graphs"
author: "Ananya Saha"
---

## Assignment

1. DAG from parking-spots example:
```{r}

library(dagitty)
library(ggdag)
library(tidyverse)

con <- dagify(
  X ~ Z,
  Y ~ Z,
  Y ~ X,
  coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 1, X = 0)),
  labels = list(X = "Parking-spot available",
                Y = "Sales",
                Z = "Customers")
)

ggdag(con) +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "white") +
  geom_dag_label_repel(aes(label = label))
```

2. Examining the data file customer_sat.rds:
```{r}
df <- readRDS("data/customer_sat.rds")
str(df)
df

# (1) regress satisfaction on follow_ups
model1 <- lm(satisfaction ~ follow_ups, data = df)
summary(model1)

# (2) regress satisfaction on follow_ups and account for subscription
model2 <- lm(satisfaction ~ follow_ups + subscription, data = df)
summary(model2)
```

3. Comparing the coefficients: coefficient for the number of follow-up calls is **negative** which implies that the satisfaction is expected to decrease if the customer receives more calls while that of follow-up calls while accounting for the subscription model is **positive**, implying that satisfaction is expected to increase with the number of calls within a given subscription model.

Perhaps the customer is having problems with more expensive subscription models. 

4. Plotting the data:
```{r}

sat_not_con <- ggplot(df, aes(x = follow_ups, y = satisfaction)) +
  geom_point() +
  stat_smooth(method = "lm", se = F)

sat_con <- ggplot(df, aes(x = follow_ups, y = satisfaction,
                            color = subscription, 
                            alpha = subscription)) +
  geom_point() +
  stat_smooth(method = "lm", se = F) +
  scale_color_manual(values = c("Elite" = "red",
                                "Premium+" = "blue",
                                "Premium" = "black")) +
  scale_alpha_manual(values = c("Elite" = 1, "Premium+" = 0.6, "Premium" = 0.2)) +
  theme(legend.position = "right")

# Displaying both plots
sat_not_con
sat_con
```