---
title: "Difference-in-Differences"
author: "Ananya Saha"
---

## Assignment

1. Manually computing the mean satisfaction for treated and control hospitals, before and after the treatment:
```{r}
library(tidyverse)
df <- readRDS("data/hospdd.rds")
str(df)

new_procedure_hospitals <- unique(df$hospital[df$procedure == 1])
new_procedure_hospitals

# satisfaction for treated hospitals before and after the treatment
treated_data <- df %>% filter(hospital %in% new_procedure_hospitals)
mean_satisfaction_treated_before <- treated_data %>% filter(month == 3) %>% summarise(mean_satisfaction = mean(satis, na.rm = TRUE)) %>% pull(mean_satisfaction)
mean_satisfaction_treated_after <- treated_data %>% filter(month == 4) %>% summarise(mean_satisfaction = mean(satis, na.rm = TRUE)) %>% pull(mean_satisfaction)

# satisfaction for control hospitals before and after the treatment
control_data <- df %>% filter(!hospital %in% new_procedure_hospitals)
mean_satisfaction_control_before <- control_data %>% filter(month == 3) %>% summarise(mean_satisfaction = mean(satis, na.rm = TRUE)) %>% pull(mean_satisfaction)
mean_satisfaction_control_after <- control_data %>% filter(month == 4) %>% summarise(mean_satisfaction = mean(satis, na.rm = TRUE)) %>% pull(mean_satisfaction)

DiD_estimate_before <- mean_satisfaction_treated_before - mean_satisfaction_control_before
DiD_estimate_after <- mean_satisfaction_treated_after - mean_satisfaction_control_after
DiD <- DiD_estimate_after - DiD_estimate_before
cat("Estimated DiD: ", DiD)
```

2. Using a linear regression to compute the estimate. Including group and time fixed effects in the regression, i.e. one regressor for each month and one regressor for each hospital: 
```{r}
model_01 <- lm(satis ~ procedure + month + hospital, data = df)
summary(model_01)

model_02 <- lm(satis ~ procedure + as.factor(month) + as.factor(hospital), data = df)
summary(model_02)
```
Explanation: Besides other visible differences between each month and hospital, the major difference is that when it is included as a factor each value becomes a category.